A load balancing scheme for massively multiplayer online games \thanks{This work was supported by the National Research Council (CNPq) and by the Coordination of Improvement of Higher Education (CAPES), both brazilian research funding agencies.}

### 2009-04-10 trunk/textos/dissertation/MTAP_LaTeX/pub/tex/latex/svjour3/global/balancing.tex

% deviation
Another detail to be considered is the uniformity of distribution: all servers must have a usage rate as similar as possible so that the distribution is considered fair. To measure this uniformity, the standard deviation, $\sigma$, was calculated for $u(S)$ of all servers for each simulated algorithm. Figure \ref{gra:baldeviation} shows the variation of $\sigma$ in time.

@@

It was proposed here a load balancing scheme for distributed MMOGs servers, taking into account the use of upload bandwidth of the server nodes. We considered important aspects such as quadratic growth in traffic when the avatars are close to one another, and the distribution overhead when players connected to different servers are interacting. The scheme, which is divided into three phases, proposed different algorithms for phase 2 (the balancing phase), and the \ggp\ presented the lowest overhead of all, while \ggpf\ presented the fewest migrations of players between servers.

>>>>

% deviation
Another detail to be considered is the uniformity of distribution: all servers must have an usage rate as similar as possible so that the distribution is considered fair. To measure this uniformity, the standard deviation, $\sigma$, was calculated for $u(S)$ of all servers for each simulated algorithm. Figure \ref{gra:baldeviation} shows the variation of $\sigma$ in time.

@@

It was proposed here a load balancing scheme for distributed MMOG servers, taking into account the use of upload bandwidth of the server nodes. We considered important aspects such as quadratic growth in traffic when the avatars are close to one another, and the distribution overhead when players connected to different servers are interacting. The scheme, which is divided into three phases, proposed different algorithms for phase 2 (the balancing phase), and the \ggp\ presented the lowest overhead of all, while \ggpf\ presented the fewest migrations of players between servers.
